Exploring and Predicting House Prices in Nanjing, China: Geographically Imbalanced Distribution Across Districts and the Crucial Role of Unit Price and Bedroom Count in Prediction

### 2023-12-20 output/paper/paper.qmd

House prices in China have grown rapidly since 2000, and prices in cities such as Shanghai, Beijing, and Shenzhen are among the highest in the world today [@citeHouseincrease]. Nanjing, which is located in the Yangtze River Delta in eastern China and approximately 300 km from Shanghai, is the capital city for Jiangsu Province, one of the most economically developed provinces in China [@citeNanjing]. House prices in Nanjing have been a concern due to increased population in recent years [@citeConcern].

@@

We used `Python` [@citePython] to obtain the datasets and `R` [@citeR] to do the analysis in this paper. We used packages `requests` [@citeRequests], `parsel` [@citeParsel], and `csv` [@citeCsv] in `Python` to scrape the data, and then in `R`, we used packages `tidyverse` [@citeTidyverse], `stringr` [@citeStringr], and `here` [@citeHere] to clean and load the data as well as create figures. We used package `latex2exp` [@citeLatex2exp] to add labels to figures, `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra], `broom` [@citeBroom], and `gt` [@citeGt] to generate tables, and `corrplot` [@citeCorrplot] to make the correlation plot. We also used package `randomForest` [@citeRandomforest] and `Metrics` [@citeMetrics] to estimate random forest model and compare the results with the multiple linear regression model using different metrics. The color style of the figures was created referring to a R colors cheet-sheet [@citeRcolor].

@@

The dataset in this analysis was obtained from Lianjia.com using a web scraping program in Python. Lianjia.com is the website of one of the largest estate brokerage firm in China and it is open and accessible [@citeLianjia]. We collected 11 datasets with 30,653 observations for 11 different districts in Nanjing, China. To account for temporal variations in the housing market, we specifically collected sales property prices listed on 22 November 2023, instead of posted transactions. To enhance the consistency, we only collected data for residential houses and discarded data for other types of properties. The datasets include listed sales prices and structural attributes of the properties such as the floor area, the unit price per $\mbox{m}^2$, district, decoration status, number of bedrooms, number of living rooms, total floor of the building, detailed floor of the house, and whether the house is south-facing.

The original datasets were merged into one large dataset by district, with missing values removed. After obtaining five detailed structural characteristics by splitting the `Structrual attributes` variable in original dataset, we created two new variables: `Detailed_Floor` and `Facing_South`. The variable `Detailed_Floor` was obtained from the variable `Total floor`. If the property is in a high floor, the detailed floor will be the total floor multiplied by 0.7; if the property is in a medium floor, the detailed floor will be the total floor multiplied by 0.45; and if the property is in a low floor, the detailed floor will be the total floor multiplied by 0.2. The variable `Facing_South` is a dummy variable with 1 representing the house is south-facing and 0 otherwise. Definitions and descriptions for the 10 variables are listed in @tbl-data. Most of them capture the structural attributes of the house and only `District` indicates an approximate location of the house.

@@

@tbl-price shows a summary for average total house price in thousand yuan, average unit price in thousand yuan/$\mbox{m}^2$, and average floor area in $\mbox{m}^2$ for 11 districts in Nanjing. We find that the highest average house price was in Jianye district while the lowest average house price was in Gaochun district, which is also consistent with the average unit price. However, the average floor area shows a different pattern. The Qinhuai district had the smallest average floor area while Jianye and Pukou districts had the largest average floor area. The difference, at 30 $\mbox{m}^2$, was not very large. This may reflect geographical information for each district since the area and population differ from each district. Different from relatively centered average floor area for each districts, the average house price and unit price show a larger variance. This may relate to business activities and industrial development in each district.

@@

We find from @fig-char that the number of houses in each district in our data were similar, excluding Gaochun district. This related to the web scraping program we used to obtain the data. However, it indicates that the total number of houses listed in Gaochun district was limited. For the orientation of the house, we find that relatively half of the houses were south-facing and in Lishui and Gaochun district the proportions were even higher. It shows a tradition in China that people tend to choose houses facing south, which according to Chinese traditional Feng Shui has positive effect on someone's luck [@citeFengshui]. For decoration status of the house, the data was not that informative since type `Other` occupies a large proportion, which means the information is missing for the house. However, from existing data we find that fully furnished houses on sale have a larger proportion than partly furnished or not furnished house. This may relate to the data we collected that there were a lot of second-hand house on sale instead of newly closed. It is noticeable that houses in the Jianyi district had a much larger proportion of fully furnished house. This may be related to the house type, as there are more fully furnished luxury apartments in Jianyi since the Central Business District (CBD) is located there.

@@

## Multiplie Linear Regression {#sec-result_mlg}

@@

In 2013, the Nanjing Government adjusted the boundaries and administrative divisions of Nanjing. Since then, there are 11 districts in Nanjing with Gulou, Qinhuai, Xuanwu, Jianye districts considered as inner proper while Qixia, Yuhuatai, Pukou, Jiangning, Lishui, Gaochun, Liuhe districts are considered as suburban areas of Nanjing [@citeDivision]. The difference in house prices between inner city and suburban areas was also revealed in this paper. From @tbl-price we find that both the average unit price and average total price in inner proper districts are much higher than that of suburban districts. The highest average total price is in the Jianye district with value of 5,406,000 while the lowest average total price is in the Gauchun district with value of 866,800. The large difference in average total price across districts indicates disparities in economical development in each districts. The average floor area in suburban districts is slighter larger than that of inner city. It is consistent with the geographical features of the districts. Suburban areas usually have more available space for real estate, and the real estate developers have difference business strategies and target consumer for inner and suburban areas. Houses in suburban areas are usually designed as two types: one is affordable housing targeted at consumers without much money for the down payment, another is luxury villas targeted at consumers who have more money. Former type of house usually has smaller floor area and lower total price due to its location and transportation convenience. Villas are designed to have larger size and better quality with good environment. As a result, we could see from @fig-area and @fig-price, both area and total price in suburban areas vary a lot within each districts especially for Pukou district. The observed variation in housing conditions not only reveals the diverse economic status but also emphasizes the potential disparities in overall quality of life within specific districts. This difference in house quality and living standards among residents within the same district reflects the broader issues of wealth and income inequality as well as social class.

The economical development in each district also contributes to the difference in house prices across districts. There are two main commercial districts in Nanjing, one in the city center in Gulou district and one in the CBD in Jianye district. Due to limited available space and large population density, high-rise condominiums and luxury apartments are two main types of housing in Gulou and Jianye. These two types of houses usually demand higher pricse due to the modern amenities and location. In addition, commercial districts are accompanied by more job opportunities and higher income level, which attracts those who are seeking more convenient living environment and houses closer to companies to shorten commuting time. The high demand for housing in commercial districts also affects the rental market, thus increasing investment enthusiasm. For Gulou district, there is a third type of house, old apartment built early in 1980s. Since it was developed early, the amenities sometimes function improperly, and management is lax and inefficient with small floor areas. However, such houses still have high total prices. This is related to their surrounding facilities especially schools. In Nanjing, public schools in the compulsory education period that a child may attend is determined by the household registration system, that is primary school and middle school [@citeEdu]. As a result, parents who wish their children to attend a better public school may choose to buy an apartment within the school district [@citeParent]. Since it was developed early, many qualified and renowned public schools are located in Gulou district, resulting in the high demand of houses in school district divisions and thus higher house prices.

@@

## Structral attributes characteristics and performace on predicting house prices {#sec-structural}

@@

Several factors contribute to the better prediction performance of random forest model. According to @fig-price and @fig-area, the relationships between `Area`, `Unit_Price`, and `Total_Price` for most districts in Nanjing are non-linear. In this case, the multiple linear regression is limited to capture non-linear relationships, thus resulting in worse predictions. Other than non-linear relationships in the dataset, we find that from @fig-cor, `Area` and `Bedroom` are highly positively correlated as well as `Total_Floors` and `Detailed_Floor`. The correlation between `Area` and `Living_Room`, and the correlation between `Bedroom` and `Living_Room` are also positive and quite large. It indicates there exists multicolineaerity in the predictors. The MLG model is sensitive to multicolinearity while the random forest model is more robust, resulting a better prediction performance of random forest model. Another concern is about outliers. Since from @fig-con, the distributions of `Total_Price`, `Area`, and `Unit_Price` are all right-skewed, the dataset contains some extremely high values and possible outliers. In this case, the random forest model is also more robust to outliers while the multiple linear regression model is more sensitive, contributing to the difference in prediction performance.

@@

This paper analyzed the characteristics of house prices and associated structural attributes as well as performing predictions, however, several limitation should be acknowledged. One limitation lies in the web scraping program used. Since the data was obtained by web scraping, the data was real-time and credible. However, the website limited maximum scraping page to be 100, which qualified the number of observations. In this case, since the houses was presented in a random order, and we got a large number of observations, our data could still be considered as representative for house prices on sale in Nanjing.

@@

For models we used in the analysis, we could also consider some improvements in future work. The validity of multiple linear regression model was challenged by the potential multicolinearity concern as shown in @fig-cor, which affected the reliability of the estimates of coefficients. Additionally, although 
the difference between performance on training data and testing data for two models was not significant, we should still be careful about overfitting. The random forest model is less prone to overfitting by ensemble learning algorithm, however, a complex tree structure may also arise the problem of overfitting. In this case, we may consider using shrinkage methods such as Lasso or Ridge regression to mitigate the problem of multicolinearity and overfitting for the multiple linear regression model. For the RF model, we did not tune hyperparameters in the model, that is the number of trees, the number of candidate predictors at each split, and the minimum size of nodes. Although the model yielded the prediction results with a relatively low MAE and RMSE and a high $R^2$, we could still enhance the model performance by tuning hyperparameters. It will also increase the robustness and generalization of the model and ensure the optimal performance.

>>>>

House prices in China have grown rapidly since 2000, and prices in cities such as Shanghai, Beijing, and Shenzhen are among the highest in the world today [@citeHouseincrease]. Nanjing, which is in the Yangtze River Delta in eastern China and approximately 300 km from Shanghai, is the capital city for Jiangsu Province, one of the most economically developed provinces in China [@citeNanjing]. House prices in Nanjing have been a concern due to increased population in recent years [@citeConcern].

@@

We used `Python` [@citePython] to obtain the datasets and `R` [@citeR] to do the analysis in this paper. We used packages `requests` [@citeRequests], `parsel` [@citeParsel], and `csv` [@citeCsv] in `Python` to scrape the data, and then in `R`, we used packages `tidyverse` [@citeTidyverse], `stringr` [@citeStringr], and `here` [@citeHere] to clean and load the data as well as create figures. We used package `latex2exp` [@citeLatex2exp] to add labels to figures, `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra], `broom` [@citeBroom], and `gt` [@citeGt] to generate tables, and `corrplot` [@citeCorrplot] to make the correlation plot. We also used package `randomForest` [@citeRandomforest] and `Metrics` [@citeMetrics] to estimate random forest model and compare the results with the multiple linear regression model using different metrics. The color style of the figures was created referring to a R colors cheat-sheet [@citeRcolor].

@@

The dataset in this analysis was obtained from Lianjia.com using a web scraping program in Python. Lianjia.com is the website of one of the largest estate brokerage firms in China and it is open and accessible [@citeLianjia]. We collected 11 datasets with 30,653 observations for 11 different districts in Nanjing, China. To account for temporal variations in the housing market, we specifically collected sales property prices listed on 22 November 2023, instead of posted transactions. To enhance the consistency, we only collected data for residential houses and discarded data for other types of properties. The datasets include listed sales prices and structural attributes of the properties such as the floor area, the unit price per $\mbox{m}^2$, district, decoration status, number of bedrooms, number of living rooms, total floor of the building, detailed floor of the house, and whether the house is south-facing.

The original datasets were merged into one large dataset by district, with missing values removed. After obtaining five detailed structural characteristics by splitting the `Structural attributes` variable in original dataset, we created two new variables: `Detailed_Floor` and `Facing_South`. The variable `Detailed_Floor` was obtained from the variable `Total floor`. If the property is in a high floor, the detailed floor will be the total floor multiplied by 0.7; if the property is in a medium floor, the detailed floor will be the total floor multiplied by 0.45; and if the property is in a low floor, the detailed floor will be the total floor multiplied by 0.2. The variable `Facing_South` is a dummy variable with 1 representing the house is south-facing and 0 otherwise. Definitions and descriptions for the 10 variables are listed in @tbl-data. Most of them capture the structural attributes of the house and only `District` indicates an approximate location of the house.

@@

@tbl-price shows a summary for average total house price in thousand yuan, average unit price in thousand yuan/$\mbox{m}^2$, and average floor area in $\mbox{m}^2$ for 11 districts in Nanjing. We find that the highest average house price was in Jianye district while the lowest average house price was in Gaochun district, which is also consistent with the average unit price. However, the average floor area shows a different pattern. The Qinhuai district had the smallest average floor area while Jianye and Pukou districts had the largest average floor area. The difference, at 30 $\mbox{m}^2$, was not very large. This may reflect geographical information for each district since the area and population differ from each district. In contrast to the average floor area for each district, the average house price and unit price show a larger variance. This may relate to business activities and industrial development in each district.

@@

We find from @fig-char that the number of houses in each district in our data were similar, excluding Gaochun district. This related to the web scraping program we used to obtain the data. However, it indicates that the total number of houses listed in Gaochun district was limited. For the orientation of the house, we find that relatively half of the houses were south-facing and in Lishui and Gaochun district the proportions were even higher. It shows a tradition in China that people tend to choose houses facing south, which according to Chinese traditional Feng Shui has positive effect on someone's luck [@citeFengshui]. For decoration status of the house, the data was not that informative since type `Other` occupies a large proportion, which means the information is missing for the house. However, from existing data we find that fully furnished houses on sale have a larger proportion than partly furnished or not furnished house. This may relate to the data we collected that there were a lot of second-hand houses on sale instead of newly closed. It is noticeable that houses in the Jianyi district had a much larger proportion of fully furnished house. This may be related to the house type, as there are more fully furnished luxury apartments in Jianyi since the Central Business District (CBD) is located there.

@@

## Multiple Linear Regression {#sec-result_mlg}

@@

In 2013, the Nanjing Government adjusted the boundaries and administrative divisions of Nanjing. Since then, there are 11 districts in Nanjing with Gulou, Qinhuai, Xuanwu, Jianye districts considered as inner proper while Qixia, Yuhuatai, Pukou, Jiangning, Lishui, Gaochun, Liuhe districts are considered as suburban areas of Nanjing [@citeDivision]. The difference in house prices between inner city and suburban areas was also revealed in this paper. From @tbl-price we find that both the average unit price and average total price in inner proper districts are much higher than that of suburban districts. The highest average total price is in the Jianye district with value of 5,406,000 while the lowest average total price is in the Gauchun district with value of 866,800. The large difference in average total price across districts indicates disparities in economical development in each district. The average floor area in suburban districts is slighter larger than that of inner city. It is consistent with the geographical features of the districts. Suburban areas usually have more available space for real estate, and the real estate developers have difference business strategies and target consumer for inner and suburban areas. Houses in suburban areas are usually designed as two types: one is affordable housing targeted at consumers without much money for the down payment, another is luxury villas targeted at consumers who have more money. Former type of house usually has smaller floor area and lower total price due to its location and transportation convenience. Villas are designed to have larger size and better quality with good environment. As a result, we could see from @fig-area and @fig-price, both area and total price in suburban areas vary a lot within each districts especially for Pukou district. The observed variation in housing conditions not only reveals the diverse economic status but also emphasizes the potential disparities in overall quality of life within specific districts. This difference in house quality and living standards among residents within the same district reflects the broader issues of wealth and income inequality as well as social class.

The economical development in each district also contributes to the difference in house prices across districts. There are two main commercial districts in Nanjing, one in the city center in Gulou district and one in the CBD in Jianye district. Due to limited available space and large population density, high-rise condominiums and luxury apartments are two main types of housing in Gulou and Jianye. These two types of houses usually demand higher prices due to the modern amenities and location. In addition, commercial districts are accompanied by more job opportunities and higher income level, which attracts those who are seeking more convenient living environment and houses closer to companies to shorten commuting time. The high demand for housing in commercial districts also affects the rental market, thus increasing investment enthusiasm. For Gulou district, there is a third type of house, old apartment built early in 1980s. Since it was developed early, the amenities sometimes function improperly, and management is lax and inefficient with small floor areas. However, such houses still have high total prices. This is related to their surrounding facilities especially schools. In Nanjing, public schools in the compulsory education period that a child may attend is determined by the household registration system, that is primary school and middle school [@citeEdu]. As a result, parents who wish their children to attend a better public school may choose to buy an apartment within the school district [@citeParent]. Since it was developed early, many qualified and renowned public schools are located in Gulou district, resulting in the high demand of houses in school district divisions and thus higher house prices.

@@

## Structural attributes characteristics and performance on predicting house prices {#sec-structural}

@@

Several factors contribute to the better prediction performance of random forest model. According to @fig-price and @fig-area, the relationships between `Area`, `Unit_Price`, and `Total_Price` for most districts in Nanjing are non-linear. In this case, the multiple linear regression is limited to capture non-linear relationships, thus resulting in worse predictions. Other than non-linear relationships in the dataset, we find that from @fig-cor, `Area` and `Bedroom` are highly positively correlated as well as `Total_Floors` and `Detailed_Floor`. The correlation between `Area` and `Living_Room`, and the correlation between `Bedroom` and `Living_Room` are also positive and quite large. It indicates there exists multicollinearity in the predictors. The MLG model is sensitive to multicollinearity while the random forest model is more robust, resulting a better prediction performance of random forest model. Another concern is about outliers. Since from @fig-con, the distributions of `Total_Price`, `Area`, and `Unit_Price` are all right-skewed, the dataset contains some extremely high values and possible outliers. In this case, the random forest model is also more robust to outliers while the multiple linear regression model is more sensitive, contributing to the difference in prediction performance.

@@

This paper analyzed the characteristics of house prices and associated structural attributes as well as performing predictions, however, several limitations should be acknowledged. One limitation lies in the web scraping program used. Since the data was obtained by web scraping, the data was real-time and credible. However, the website limited maximum scraping page to be 100, which qualified the number of observations. In this case, since the houses was presented in a random order, and we got a large number of observations, our data could still be considered as representative for house prices on sale in Nanjing.

@@

For models we used in the analysis, we could also consider some improvements in future work. The validity of multiple linear regression model was challenged by the potential multicollinearity concern as shown in @fig-cor, which affected the reliability of the estimates of coefficients. Additionally, although 
the difference between performance on training data and testing data for two models was not significant, we should still be careful about overfitting. The random forest model is less prone to overfitting by ensemble learning algorithm, however, a complex tree structure may also arise the problem of overfitting. In this case, we may consider using shrinkage methods such as Lasso or Ridge regression to mitigate the problem of multicollinearity and overfitting for the multiple linear regression model. For the RF model, we did not tune hyperparameters in the model, that is the number of trees, the number of candidate predictors at each split, and the minimum size of nodes. Although the model yielded the prediction results with a relatively low MAE and RMSE and a high $R^2$, we could still enhance the model performance by tuning hyperparameters. It will also increase the robustness and generalization of the model and ensure the optimal performance.
